Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
Remove footnote.

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes\footnote{Python does not actually
distinguish between public and private  attributes or methods. By convention
however, any identifier prefixed with an underscore is considered a non-public
part of the API~\citep{pythontut}.} and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, default hyper-parameter values are provided for all
built-in estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible \textit{out-of-box}
for non-experts. Finally, the constructor of an estimator never performs
any actual learning, nor does it even see any training dataset. Its only goal is
to set the parameter values and freeze the behavior of the estimator.

>>>>

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, default hyper-parameter values are provided for all built-in
estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible
\textit{out-of-box} for non-experts. Finally, the constructor of an estimator
never performs any actual learning, nor does it even see any training dataset.
Its only goal is to set the parameter values and freeze the behavior of the
estimator.
